Glyph-maps for visualizing climate data and models

### 2011-08-25 paper.tex
fixing spelling

\title{Glyph-maps for visualising climate data and models}
\author{Cook, Hofmann, Wickham, Wickham, Cheng}

@@

Need a colourful map, facetted by year \& month

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{ref-line}%
  \includegraphics[width=0.5\linewidth]{ref-box}
  \caption{caption}
  \label{fig:ref-basic}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{ref-max-1}%
    \includegraphics[width=0.5\linewidth]{ref-max-2}
  \caption{caption}
  \label{fig:ref-adv}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=2in]{month-cartesian}
  \includegraphics[width=2in]{month-polar}

@@

So far we have limited ourselves to always mapping some aspect of time on the x-axis. But the method is much more general. Figure~\ref{fig:cloud} shows how by mapping another variable to the x-axis, in this case low-cloud level on x and high-cloud level on y, we can explore how this 2d distribution varies over space. Again, summarising the data with models is very useful: the second plot displays a loess curve fit to the data instead of the individual points.

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{clouds}%
    \includegraphics[width=0.5\linewidth]{clouds-smooth}
  \caption{caption}
  \label{fig:cloud}
\end{figure}

\begin{figure}[htbp]
  \centering
    \includegraphics[width=0.5\linewidth]{clouds-heike}%
  \caption{Just as an alternative: shaded map instead of the outlines. }
  \label{fig:cloud-alt}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  \includegraphics[width=0.5\linewidth]{month-rescale-max}%
  \includegraphics[width=0.5\linewidth]{month-rescale01}
  \caption{caption}
  \label{fig:label}
\end{figure}

Other types of scaling: scale range to 0-1 (subtract min and divide by range), standardise mean and standard deviation (or robust variants).

>>>>

\title{Glyph-maps for visualizing climate data and models}
\author{Cook, Hofmann, Wickham, Wickham, Cheng}

@@

Need a colorful map, facetted by year \& month

@@

\begin{figure}[htbp]
  \centering
  %\includegraphics[width=0.5\linewidth]{ref-line}%
  %\includegraphics[width=0.5\linewidth]{ref-box}
  \caption{caption}
  \label{fig:ref-basic}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
    %\includegraphics[width=0.5\linewidth]{ref-max-1}%
    %\includegraphics[width=0.5\linewidth]{ref-max-2}
  \caption{caption}
  \label{fig:ref-adv}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  %\includegraphics[width=2in]{month-cartesian}
  %\includegraphics[width=2in]{month-polar}

@@

So far we have limited ourselves to always mapping some aspect of time on the x-axis. But the method is much more general. Figure~\ref{fig:cloud} shows how by mapping another variable to the x-axis, in this case low-cloud level on x and high-cloud level on y, we can explore how this 2d distribution varies over space. Again, summarizing the data with models is very useful: the second plot displays a loess curve fit to the data instead of the individual points.

\begin{figure}[htbp]
  \centering
   % \includegraphics[width=0.5\linewidth]{clouds}%
    %\includegraphics[width=0.5\linewidth]{clouds-smooth}
  \caption{caption}
  \label{fig:cloud}
\end{figure}

\begin{figure}[htbp]
  \centering
    %\includegraphics[width=0.5\linewidth]{clouds-heike}%
  \caption{Just as an alternative: shaded map instead of the outlines. }
  \label{fig:cloud-alt}
\end{figure}

@@

\begin{figure}[htbp]
  \centering
  %\includegraphics[width=0.5\linewidth]{month-rescale-max}%
  %\includegraphics[width=0.5\linewidth]{month-rescale01}
  \caption{caption}
  \label{fig:label}
\end{figure}

Other types of scaling: scale range to 0-1 (subtract min and divide by range), standardize mean and standard deviation (or robust variants).
